Search-based Synthesis of Network Intrusion Detection Rules

### 2019-10-03 paper/paper.tex
minor comments

@@

\tname{} uses a modified version of Suricata to measure distance. It
updates the rule set that the modified version of Suricata analyses,
injects the traffic on the network, and monitors the execution. Each
rule option has an associated \CodeIn{eval} function in code. \tname{}
monitors the execution of these functions to identify how far it is
from returning true, which indicates it is closer to trigger the
action associated with the rule. For the example above,
\Fix{Lucas/Guilherme, it would be good to show how this looks like in
  code}

>>>>

\Luc{entrada: conjunto de 20 pacotes SYN que representam o flood.
tempo para gerar a regra: ~1m30s
no caso do syn flood, geramos a mesma regra.
}

@@

\tname{} uses a modified version of Suricata to measure distance. It
updates the rule set that the modified version of Suricata analyses,
injects the traffic on the network, and monitors the execution. Each
rule option has an associated \CodeIn{eval} function in code. \tname{}
monitors the execution of these functions to identify how far it is
from returning true, which indicates it is closer to trigger the
action associated with the rule. \Luc{Para opções cujos valores são numéricos, o suricata apenas verifica se o valor da opção no pacote é igual/maior/menor ao valor especificado na regra, retornando um booleano indicando isso. Alteramos o codigo fonte para obter a diferença entre o valor da opção no pacote e o valor da opção na regra.}
\Fix{Lucas/Guilherme, it would be good to show how this looks like in
  code}
